CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Improve classifier results tables

\begin{tabular}{llrrrrrrrrr}
Features & Threshold & Acc & Prec & Rec & F$_{\text{1}}$ & F$_{\text{0.5}}$ & TP & FP & FN & TN\\
\hline
p,P$_{\text{1}}$,P$_{\text{3}}$ & default & 95.44 & 89.05 & 75.74 & 81.86 & 86.03 & 3953 & 486 & 1266 & 32712\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & precision & 94.99 & 91.65 & 69.44 & 79.01 & 86.14 & 3624 & 330 & 1595 & 32868\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & max precision & 92.10 & 95.80 & 43.74 & 60.06 & 77.38 & 2283 & 100 & 2936 & 33098\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & recall & 94.28 & 73.82 & 89.65 & 80.97 & 76.53 & 4679 & 1659 & 540 & 31539\\
\end{tabular}

%}
\caption{Results of classifier using different score thresholds.}
\label{tbl:classifier-results-linear}
\end{table*}

@@

\begin{tabular}{llrrrrrrrrr}
Features & Threshold & Acc & Prec & Rec & F$_{\text{1}}$ & F$_{\text{0.5}}$ & TP & FP & FN & TN\\
\hline
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & default & 97.47 & 92.17 & 88.91 & 90.51 & 91.50 & 4640 & 394 & 579 & 32804\\
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & precision & 97.27 & 92.95 & 86.43 & 89.58 & 91.57 & 4511 & 342 & 708 & 32856\\
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & max precision & 96.57 & 94.22 & 79.63 & 86.31 & 90.89 & 4156 & 255 & 1063 & 32943\\
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & recall & 97.15 & 88.16 & 91.32 & 89.71 & 88.78 & 4766 & 640 & 453 & 32558\\
\end{tabular}

>>>>

\begin{tabular}{llrrrrrrrrr}
{\bf Features} & {\bf Threshold} & {\bf Acc} & {\bf Prec} & {\bf Rec} & {\bf F$_{\text{1}}$} & {\bf F$_{\text{0.5}}$} & {\bf TP} & {\bf FP} & {\bf FN} & {\bf TN} \\
\hline
p,P$_{\text{1}}$,P$_{\text{3}}$ & default & 95.44 & 89.05 & 75.74 & 81.86 & 86.03 & 3953 & 486 & 1266 & 32712\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & precision & 94.99 & 91.65 & 69.44 & 79.01 & 86.14 & 3624 & 330 & 1595 & 32868\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & max precision & 92.10 & 95.80 & 43.74 & 60.06 & 77.38 & 2283 & 100 & 2936 & 33098\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & recall & 94.28 & 73.82 & 89.65 & 80.97 & 76.53 & 4679 & 1659 & 540 & 31539\\
\end{tabular}

%}
\caption{Results of linear classifier using different score thresholds.}
\label{tbl:classifier-results-linear}
\end{table*}

@@

\begin{tabular}{llrrrrrrrrr}
{\bf Features} & {\bf Threshold} & {\bf Acc} & {\bf Prec} & {\bf Rec} & {\bf F$_{\text{1}}$} & {\bf F$_{\text{0.5}}$} & {\bf TP} & {\bf FP} & {\bf FN} & {\bf TN} \\
\hline
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & default & 97.47 & 92.17 & 88.91 & 90.51 & 91.50 & 4640 & 394 & 579 & 32804\\
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & precision & 97.27 & 92.95 & 86.43 & 89.58 & 91.57 & 4511 & 342 & 708 & 32856\\
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & max precision & 96.57 & 94.22 & 79.63 & 86.31 & 90.89 & 4156 & 255 & 1063 & 32943\\
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & recall & 97.15 & 88.16 & 91.32 & 89.71 & 88.78 & 4766 & 640 & 453 & 32558\\
\end{tabular}
